\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Structure-Preserving Mutations

### 2022-03-08 papers/fse22/main.tex
NIT

This approach allows \mutagen to automatically control amount of effort put into
mutating subexpressions defined using random mutations.
%
This can be especially useful to avoid putting unnecessary effort when the
execution of testing property and the system under test is independent from
their concrete values.

>>>>

\noindent This approach allows \mutagen to selectively control the amount of
effort put into mutating any subexpression of an input test case whose type is
associated to a random mutation.
%
This can be especially useful to avoid putting unnecessary effort into mutating
data payloads when the execution of testing property and the system under test
is independent from their concrete values (see \S \ref{sec:heuristics}).
